\chapter{Architectural Design}
Having an architectural design structure is essential for a system development. The purpose of having this design, is to ensure all the necessary components of the system are laid out, in a clear and understandable manner. In this chapter, the proposed architectural design is described. 

\section{Criteria}
 To get a better understanding of the design priorities of the project, a criteria prioritisation is made. 
\\\\
\resizebox{\columnwidth}{!}{%
\begin{tabu}[H]{|l|l|l|l|l|l|}
\hline
\textit{Criterion} & \textit{Very important} & \textit{Important} & \textit{Less important} & \textit{Irrelevant} & \textit{Easily fulfilled} \\ \hline
Usability             & X                       &                    &                         &                     &                           \\ \hline
Security             &                         &                    &                         &                     & X                         \\ \hline
Efficiency          &                         &                    & X                       &                     &                           \\ \hline
Correctness            &                         &                    & X                       &                     &                           \\ \hline
Reliability           & X                       &                    &                         &                     &                           \\ \hline
Maintainability       &                         &                    & X                       &                     &                           \\ \hline
Testability           &                         & X                  &                         &                     &                           \\ \hline
Flexibility           &                         &                    &                         & X                   &                           \\ \hline
Comprehensibility     & X                       &                    &                         &                     &                           \\ \hline
Reusability           &                         &                    &                         & X                   &                           \\ \hline
Portability           &                         &                    &                         &                     & X                         \\ \hline
Interoperability      &                         &                    & X                       &                     &                           \\ \hline
\end{tabu}
}
\\\\
As seen on the table the three most important criteria are usability, reliability and comprehensibility. Usability is considered very important, because it is the client's main requirement. Reliability is also prioritised because the system will help the client predict which leads are most profitable, and thus needs to predict correctly.
Lastly, making the project comprehensible is a top priority, because people who are working on coding the project needs a full understanding of the code. Moreover, the final result also needs to be comprehensible by end users.
\\
Testability is important because it has the possibility of improving development of the entire project and its final result. Testability can potentially improve usability and reliability through successful tests. Testability is necessary for the development cycle that has been chosen for this project, where repeated user testing throughout development is a crucial part of creating the final product.
\\
Interoperability is less important, because none of the features that requires communication with another system are must have or should have.
Correctness has been chosen as less important, because there are a lot of requirements and it will be impossible to fulfill them all, within the scope of the project. Efficiency has not been prioritised, because the system has no time sensitive tasks.
\\
Flexibility and reusability are irrelevant, because there are no plans to continue development, beyond the scope of this project. Maintainability is still less important, because it help fixing the errors that appears during testing in the iterative cycles.
\\
%Måske skriv om andre?

Security and portability are both easily fulfilled, due to the framework chosen for development. Portability because it is a webpage, and is thus accessible though all devices with a modern webbrowser. Security due to the frameworks built in option for https, with should encrypt all data going between the user and the system.


\section{Components}

\section{Processes}

\section{FULDT KLASSEDIAGRAM?}

\section{DATABASE OPSÆTNING?}

\section{Summary}
Der skal skrives en afrunding af kap. her